Open-source landscape for 3D CSEM modelling

### 2020-09-15 manuscript/Manuscript.tex
MarlimR3d responses figures

The block model is a derivation of the \emph{Dublin Test Model 1} from the first EM modelling workshop described by \cite{GJI.13.Miensopust}. We took the same layout of the blocks but adjusted the dimensions and resistivities to a typical marine CSEM problem, as shown in Figure~\ref{fig:block-model}. We additionally added a layered background with vertical transverse isotropy (VTI).
%
\plot*{block-model}{width=.6\textwidth}{
  Sketch of the block model. The layered model consists of an air layer, a water layer, a thin top-layer followed by a thick, anisotropic background layer, and at the bottom a resistive basement layer. All three blocks are embedded in the thick background layer, which has VTI with $\lambda=\sqrt{2}$.
}
%

In a second step, three resistive blocks were added in the 2.3\,km-thick, anisotropic background layer as shown in Figure~\ref{fig:block-model}. They have resistivities of $\rho=10\,\ohmm$ (shallow beam perpendicular to survey lines), $\rho=100\,\ohmm$ (thin plate, South-East), and $\rho=500\,\ohmm$ (cube, North-West). As there are no (semi-)analytical solutions for this model we use the normalised root-mean square difference (NRMSD) between different codes, where the NRMSD of two responses $p$ and $q$ is given by
%
\begin{equation}
  \mr{NRMSD~(\%)} = 200 \frac{|p - q|}{|p| + |q|}\ .
  \label{eq:nrmsd}
\end{equation}
%
\imycom[DW]{NRMSD: Comparing all codes to all would make the figures too cluttered, and I don't think it would add a lot insights. My idea is therefore to compare \emg3d/\simpeg (the two FV ones), \custem/\petgem (the two FE ones), and \emg3d/\custem (a cross-comparison). What do you think?

@@

%
\plot*{median-stats-block}{width=\textwidth}{
  {\imycom[DW]{Suggestion from Raphael for a statistics plot.}}
    Overall misfit relations between all codes for the three receiver lines
    y=-3, y=0, and y=3 (f.l.t.r.). Colors indicate the median values of the 101
    calculated NRMSD arguments for each line between all codes. Errors for real
    parts are shown in the lower triangle, for imaginary parts in the upper
  triangle.
}
%

@@

We computed all all six frequencies for all components ($E_x$, $E_y$, $E_z$) for both inline and broadside acquisition lines. However, we show here only the three frequencies and the responses with the strongest amplitudes (which are generally used in processing), which are $E_x$ inline and broadside, and $E_y$ broadside. The comparison is shown in Figure~\ref{fig:results-marlim}.
%
\plot*{results-marlim}{width=\textwidth}{
  This is one heck of a figure. Just an idea, please make suggestions how to
  improve it (currently, \petgem data is a copy of \custem data, and \simpeg
  data is a copy of \emg3d data).
}
%

>>>>

The block model is a derivation of the \emph{Dublin Test Model 1} from the first EM modelling workshop described by \cite{GJI.13.Miensopust}. We took the same layout of the blocks but adjusted the dimensions and resistivities to a typical marine CSEM problem, as shown in Figure~\ref{fig:model-block}. We additionally added a layered background with vertical transverse isotropy (VTI).
%
\plot*{model-block}{width=.6\textwidth}{
  Sketch of the block model. The layered model consists of an air layer, a water layer, a thin top-layer followed by a thick, anisotropic background layer, and at the bottom a resistive basement layer. All three blocks are embedded in the thick background layer, which has VTI with $\lambda=\sqrt{2}$.
}
%

In a second step, three resistive blocks were added in the 2.3\,km-thick, anisotropic background layer as shown in Figure~\ref{fig:model-block}. They have resistivities of $\rho=10\,\ohmm$ (shallow beam perpendicular to survey lines), $\rho=100\,\ohmm$ (thin plate, South-East), and $\rho=500\,\ohmm$ (cube, North-West). As there are no (semi-)analytical solutions for this model we use the normalised root-mean square difference (NRMSD) between different codes, where the NRMSD of two responses $p$ and $q$ is given by
%
\begin{equation}
  \mr{NRMSD~(\%)} = 200 \frac{|p - q|}{|p| + |q|}\ .
  \label{eq:nrmsd}
\end{equation}
%
\imycom[DW]{NRMSD: Comparing all codes to all would make the figures too cluttered, and I don't think it would add a lot insights. My idea is therefore to compare \emg3d/\simpeg (the two FV ones), \custem/\petgem (the two FE ones), and \emg3d/\custem (a cross-comparison). What do you think?

@@

@@

We computed all all six frequencies for all components ($E_x$, $E_y$, $E_z$) for both inline and broadside acquisition lines. However, we show here only the three frequencies and the responses with the strongest amplitudes (which are generally used in processing), which are $E_x$ inline and broadside, and $E_y$ broadside. The comparison is shown in Figure~\ref{fig:results-marlim}.

%
\plot*{results-marlim-responses}{width=\textwidth}{
}
%

%
\plot*{results-marlim_2published}{width=\textwidth}{
  This is one heck of a figure. Just an idea, please make suggestions how to
  improve it (currently, \petgem data is a copy of \custem data, and \simpeg
  data is a copy of \emg3d data).
}
%

%
\plot*{results-marlim_2ours}{width=\textwidth}{
}
%

%
\plot*{results-marlim_entire}{width=\textwidth}{
}
%
%
\plot*{results-marlim_survey}{width=\textwidth}{
}
%
